---
title: "Prueba"
author: "Raquel"
date: "10/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

Wildfires and post-fire burnt-wood management treatments disturb the soils of forest ecosystems. However, little
attention has been paid to the impact of these compound disturbances from a medium- to long-term perspective.
In this study, we compared the decadal effect on soil carbon and nutrient concentrations (i.e. C, N, K and P) of
two post-fire burnt wood treatments that differed in management intensity. We established two blocks differing
in elevation, each including three replicates (ca. 3 ha) of each of two treatments: salvage logging (SL), a treatment
that emulated a conventional salvage logging (although logs of dead wood were stacked within-plots in
piles covering < 5% of the area), and a treatment where 90% of the burnt trees were manually cut but all biomass
was haphazardly spread over the ground (partial cut, PC). Soil carbon and nutrient concentrations were
compared across treatments, across the bare soil of both treatments, and in areas of bare soil versus areas below
burnt trunks within the PC treatment. All analyzed soil chemical properties differed between elevation blocks.
Moreover, C, K and P concentrations were higher in the PC treatment than in the SL treatment, although effect
sizes were small. Similarly, C and P were higher in the bare soil of the PC treatment than in the bare soil of the SL
treatment. However, the soil away from logs and the soil underneath logs did not show significant differences for
C, N, K and P concentrations within the PC treatment, suggesting that scattered dead wood originated a higher
log cover that physically protects the soil and enhances nutrient availability. Our findings indicate that, a decade
after wildfire and treatment implementation, salvage logging produced lower soil carbon and nutrient concentrations
than another management treatment which left all wood scattered over the ground. Studying the longlasting
impacts of post-fire management strategies is essential to propose suitable management approaches that
contribute to recover soil nutrient availability.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
